---
title: "Ggplot2 Exercises - 2"
Author: Macarena L. Fernandez Carro
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here: Macarena



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
cces$ideo5[cces$ideo5 == 1] <- "Very Liberal"
cces$ideo5[cces$ideo5 == 2] <- "Liberal"
cces$ideo5[cces$ideo5 == 3] <- "Moderate"
cces$ideo5[cces$ideo5 == 4] <- "Conservative"
cces$ideo5[cces$ideo5 == 5] <- "Very Conservative"
names(cces)[11] <- paste("Ideology")

cces$pew_religimp[cces$pew_religimp == 1] <- "Very Imp."
cces$pew_religimp[cces$pew_religimp == 2] <- "Somewhat Imp."
cces$pew_religimp[cces$pew_religimp == 3] <- "Not too Imp."
cces$pew_religimp[cces$pew_religimp == 4] <- "Not at all Imp."

ggplot(cces) +
  geom_bar(aes(x = Ideology,
               fill = Ideology)) +
  theme(legend.position = "none") +
  labs(title = "Respondent Ideology",
       x = "Ideology",
       y = "Count")
```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
ggplot(cces) +
  geom_bar(aes(x = pew_religimp,
               fill = Ideology))+
  labs(title = "Importance of Religion by Ideology",
       x = "Importance of Religion",
       y = "Count")
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
set.seed(1234)

Grades <- 
  tibble(
    Semester = 1:6 %>% rep(times = 3),
    Student = c("Amada", "Betty", "Carol") %>% rep(each = 6),
    Grade = runif(18, 80, 100)
  )
Grades

ggplot(Grades) +
  geom_line(aes(x = Semester,
                y = Grade,
                color = Student)) +
  facet_wrap(~Student) +
  theme(legend.position = "none")

```
